Delay Comparison of Different Switch Architectures

### 2013-11-02 MSReport/MSThesis.tex
Updated ack behavior and improved garphing tools.  Some flow queues get really hosed in this simulation -- although all the switch queues are fine -- still trying to diagnose why.

% make the title area
\maketitle

>>>>

% make the title area

\maketitle

{\abstract
 We compare slip and qcsma, find that considering packet size difference is very important to take into consideration.
\begin{itemize}
\item Metric is Delay (makes sense in DataCenter Environments)
\item Delay VS Throughput result changes dramatically depending on packet size assumptions
\item TCP acts as expected
\end{itemize}
}

\section{Introduction}
\begin{itemize}
\item Routers are a core piece of our networks
\item Need simple scheduling policies, since volume of traffic strongly penalizes per packet overheads 
\item In the internet throughput is right metric -- can't make up for other delays in network
\item In Data centers have enough control over other switches that delay becomes a good metric.
\item Evolution of Routers -- SLIP killed head of Line delays but can't really be analyzed
\item QCSMA -- solves NP hard problem, but may cause large delays?
\item Question:  Should the optimality of QCSMA not show up in some performance gains over slip?  (In particular wrt delay?)
\end{itemize}

\section{Schedulers}
\begin{itemize}
\item How they work
\item Design Philosophy
\item Expected Properties
\end{itemize}

\section{Experiments}
\begin{itemize}
\item Uniform Packet Sizes VS 
\item Design Philosophy
\item Expected Properties
\end{itemize}
